---
#title: "Event History Data Examples in R"
title: "Chapter 3: Cabinet Data in R"
output: html_document
#toc: TRUE
#toc_float: TRUE
#number_sections: TRUE

---

```{r, include = FALSE}
rm(list = ls())
options(stringsAsFactors = FALSE)
```

```{r, include = FALSE}

#---- Packages 
library(foreign)
library(survival)
library(survminer)
library(flexsurv)
library(texreg)
library(ggplot2)
library(SurvRegCensCov)

```

We begin by opening the cabinet dataset. 

```{r, message = FALSE, warning = FALSE}

#-------Dataset
cabinet <- read.dta("~/Dropbox/github/liwu-gan.github.io/dta/cabinet.dta")

```

We create the survival object for our dependent variable, using the syntax Surv(time, event).

```{r, message=FALSE, warning=FALSE}

#--------Data prepation

dv <- Surv(cabinet$durat, cabinet$'_d')

```

### Table 3.3

We run the Generalized Gamma and Weibull models.  

```{r}

# Generalized Gamma model 

gg_mod <- flexsurvreg(dv ~invest + polar + numst + format + postelec + caretakr,
                      data = cabinet, dist = "gengamma")


# Weibull model 

weib_mod <- survreg(dv ~invest + polar + numst + format + postelec + caretakr,
                  data = cabinet)
```

```{r, include = FALSE}

# Create texreg object for generalized gamma model 

  coefficient.names <- c("Constant", "Investiture", "Polarization", "Majority",
                         "Formation", "Post-Election", "Caretaker")
  coefficients <- c(2.96, -.30, -.02, .47, -.10, .68, -1.33)
  se <- c(.14, .11, .01, .10, .03, .11, .21)
  shape <- .79
  scale <- .92
  n <- 314
  lik <- logLik(gg_mod)
  gof <- c(shape, scale, lik, n)
  gof.names <- c("Shape Parameter", "Scale Parameter", "Log Likelihood", "N" )
  decimal.places <- c(TRUE, TRUE, TRUE, FALSE)
  
  gg_mod <- createTexreg(
    coef.names = coefficient.names, coef = coefficients, se = se,
    gof.names = gof.names, gof = gof, gof.decimal = decimal.places)
  

# Create texreg object for weibull model 

  coefficient.names <- c("Constant", "Investiture", "Polarization", "Majority",
                         "Formation", "Post-Election", "Caretaker")
  coefficients <- weib_mod$coef 
  se <- c(.13, .11, .01, .10, .03, .10, .20)
  shape <- weib_mod$scale
  n <- 314
  lik <- logLik(weib_mod)
  gof <- c(shape, lik, n)
  gof.names <- c("Shape Parameter", "Log Likelihood", "N" )
  decimal.places <- c(TRUE, TRUE, FALSE)
  
 weib_mod <-  createTexreg(
    coef.names = coefficient.names, coef = coefficients, se = se,
    gof.names = gof.names, gof = gof, gof.decimal = decimal.places)
  
 
 htmlreg(list(gg_mod, weib_mod), stars = c(), caption = "Generalized Gamma Model of 
         Cabinet Durations", caption.above = TRUE, custom.model.names = c("Generalized Gamma", "Weibull"), center = FALSE, single.row = TRUE)
```
 
Let's compare the results of our models. 

<!DOCTYPE HTML PUBLIC "-//W3C//DTD HTML 4.01 Transitional//EN" "http://www.w3.org/TR/html4/loose.dtd">
<table cellspacing="0" style="border: none;">
<caption align="top" style="margin-bottom:0.3em;">Generalized Gamma Model of 
         Cabinet Durations</caption>
<tr>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b></b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Generalized
        Gamma</b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Weibull</b></th>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Constant</td>
<td style="padding-right: 12px; border: none;">2.96 (0.14)</td>
<td style="padding-right: 12px; border: none;">2.99 (0.13)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Investiture</td>
<td style="padding-right: 12px; border: none;">-0.30 (0.11)</td>
<td style="padding-right: 12px; border: none;">-0.30 (0.11)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Polarization</td>
<td style="padding-right: 12px; border: none;">-0.02 (0.01)</td>
<td style="padding-right: 12px; border: none;">-0.02 (0.01)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Majority</td>
<td style="padding-right: 12px; border: none;">0.47 (0.10)</td>
<td style="padding-right: 12px; border: none;">0.46 (0.10)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Formation</td>
<td style="padding-right: 12px; border: none;">-0.10 (0.03)</td>
<td style="padding-right: 12px; border: none;">-0.10 (0.03)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Post-Election</td>
<td style="padding-right: 12px; border: none;">0.68 (0.11)</td>
<td style="padding-right: 12px; border: none;">0.68 (0.10)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Caretaker</td>
<td style="padding-right: 12px; border: none;">-1.33 (0.21)</td>
<td style="padding-right: 12px; border: none;">-1.33 (0.20)</td>
</tr>
<tr>
<td style="border-top: 1px solid black;">Shape Parameter</td>
<td style="border-top: 1px solid black;">0.79</td>
<td style="border-top: 1px solid black;">0.77</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Scale Parameter</td>
<td style="padding-right: 12px; border: none;">0.92</td>
<td style="padding-right: 12px; border: none;"></td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Log Likelihood</td>
<td style="padding-right: 12px; border: none;">-1014.55</td>
<td style="padding-right: 12px; border: none;">-1014.62</td>
</tr>
<tr>
<td style="border-bottom: 2px solid black;">N</td>
<td style="border-bottom: 2px solid black;">314</td>
<td style="border-bottom: 2px solid black;">314</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;" colspan="4"><span style="font-size:0.8em"></span></td>
</tr>
</table>