---
title: "Conflict Data in R"
output: html_document
---
```{r, include = FALSE}

#---- Packages 
library(foreign)
library(survival)
library(survminer)
library(flexsurv)
library(texreg)
library(ggplot2)
library(SurvRegCensCov)
library(haven)
library(eha)
library(tidyverse)

```



```{r}

#-------Dataset

conflict <- read.dta("~/Dropbox/github/liwu-gan.github.io/dta/conflict.dta")

dv <- Surv(conflict$start, conflict$duration, conflict$dispute)

```



### Table 9.1

I run two models: a regular Cox model and one with an individual-level gamma frailty term. Because our unit of observation is at the dyad level, the frailty term will capture any unobserved heterogeneity arising from each observation that is not picked up by the explanatory variables. If the variance of the frailty is 0, we can accept the null hypothesis that there is no unobserved heterogeneity. As it is clearly not 0 and is statistically significant, we cat reject the hypothesis that there is no unobserved heterogeneity. As such, the results indicate that there is substantial heterogeneity in the data that is not accounted for by the six covariates. 

```{r}

# Cox model

cox_mod <- coxph(dv ~ democ + growth + allies + contig + capratio + trade,
                 data = conflict, robust = TRUE)


# Cox model with frailty term 

frail_mod <- coxph(dv ~ democ + growth + allies + contig + capratio + trade
                     + frailty(dyadid, dist = "gamma"), data = conflict)

```

```{r, include = FALSE}

# Write function to customize model output for both models, starting with Cox 

tex_reg_converter <- function(original_model){
  
  
  coefficient.names <- c("Democracy", "Growth", "Alliance", "Contiguous",
                         "Capability Ratio", "Trade")
  coefficients <- original_model$coef 
  se <- sqrt(diag(vcov(original_model)))
  n <- original_model$n
  gof <- n
  gof.names <- "N"
  decimal.places <- FALSE
  
  createTexreg(
    coef.names = coefficient.names, coef = coefficients, se = se,
    gof.names = gof.names, gof = gof, gof.decimal = decimal.places)
  
}

cox_mod <- tex_reg_converter(cox_mod)

# I will do the Cox with Gamma Frailty by hand since it is more tricky to extract what I need 

coefficient.names <- c("Democracy", "Growth", "Alliance", "Contiguous",
                       "Capability Ratio", "Trade", "Variance of the Random Effect")
coefficients <- c(-0.37, -3.69, -.37, 1.20, -0.20, -3.04, 708.94) 
se <- c(.11, 1.30, .13, .13, 0.05, 10.31, 0)
n <- frail_mod$n
gof <- n
gof.names <- "N"
decimal.places <- FALSE

frail_mod <- createTexreg(
  coef.names = coefficient.names, coef = coefficients, se = se,
  gof.names = gof.names, gof = gof, gof.decimal = decimal.places)


```

Here is the output, with the standard errors in parentheses:

```{r, include = FALSE}
# Put tables all together

htmlreg(list(cox_mod, frail_mod), stars = c(), caption = "Frailty Model of Conflict", caption.above = TRUE, custom.model.names = c("Cox", "Cox with Gamma Frailty"), single.row = TRUE)

```

<!DOCTYPE HTML PUBLIC "-//W3C//DTD HTML 4.01 Transitional//EN" "http://www.w3.org/TR/html4/loose.dtd">
<table cellspacing="0" align="center" style="border: none;">
<caption align="top" style="margin-bottom:0.3em;">Frailty Model of Conflict</caption>
<tr>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b></b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Cox</b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Cox with Gamma Frailty</b></th>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Democracy</td>
<td style="padding-right: 12px; border: none;">-0.44 (0.10)</td>
<td style="padding-right: 12px; border: none;">-0.37 (0.11)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Growth</td>
<td style="padding-right: 12px; border: none;">-3.23 (1.30)</td>
<td style="padding-right: 12px; border: none;">-3.69 (1.30)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Alliance</td>
<td style="padding-right: 12px; border: none;">-0.41 (0.11)</td>
<td style="padding-right: 12px; border: none;">-0.37 (0.13)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Contiguous</td>
<td style="padding-right: 12px; border: none;">1.21 (0.13)</td>
<td style="padding-right: 12px; border: none;">1.20 (0.13)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Capability Ratio</td>
<td style="padding-right: 12px; border: none;">-0.21 (0.06)</td>
<td style="padding-right: 12px; border: none;">-0.20 (0.05)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Trade</td>
<td style="padding-right: 12px; border: none;">-13.16 (11.41)</td>
<td style="padding-right: 12px; border: none;">-3.04 (10.31)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Variance of the Random Effect</td>
<td style="padding-right: 12px; border: none;"></td>
<td style="padding-right: 12px; border: none;">708.95 (0.00)</td>
</tr>
<tr>
<td style="border-top: 1px solid black;">N</td>
<td style="border-top: 1px solid black;">20448</td>
<td style="border-top: 1px solid black;">20448</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;" colspan="4"><span style="font-size:0.8em"></span></td>
</tr>
</table>