---
#title: "Event History Data Examples in R"
title: "Chapter 4: Cabinet Data in R"
output: html_document
#toc: TRUE
#toc_float: TRUE
#number_sections: TRUE

---
```{r, include = FALSE}
rm(list = ls())
options(stringsAsFactors = FALSE)
```

```{r, include = FALSE}

#---- Packages 
library(foreign)
library(survival)
library(survminer)
library(flexsurv)
library(texreg)
library(ggplot2)
library(gridExtra)
library(SurvRegCensCov)

```

```{r, include = FALSE}

#-------Dataset
cabinet <- read.dta("~/Dropbox/github/liwu-gan.github.io/dta/cabinet.dta")

#--------Data prepation

dv <- Surv(cabinet$durat, cabinet$'_d')

```


### Table 4.4
First, we run each of the models. 
```{r}
# Run Cox model with the Breslow approximation
b_mod <- coxph(dv ~ invest + polar + numst + format + postelec + caretakr,
               data = cabinet, ties = "breslow")

# Run Cox model with the Efron approximation

ef_mod <- coxph(dv ~ invest + polar + numst + format + postelec + caretakr,
                data = cabinet)

# Run Cox model with the Exact Discrete apprximation 

ed_mod <- coxph(dv ~ invest + polar + numst + format + postelec + caretakr,
                data = cabinet, ties = "exact")


```


```{r, include = FALSE}
# Write function to customize model output for all three models 


tex_reg_converter <- function(original_model){
  
  
  coefficient.names <- c("Investiture", "Polarization", "Majority", "Formation", "Post-Election",
                         "Caretaker")
  coefficients <- original_model$coef 
  se <- sqrt(diag(vcov(original_model)))
  n <- original_model$n
  lik <- logLik(original_model)
  gof <- c(lik, n)
  gof.names <- c("Log Likelihood", "N" )
  decimal.places <- c(TRUE, FALSE)
  
  createTexreg(
    coef.names = coefficient.names, coef = coefficients, se = se,
    gof.names = gof.names, gof = gof, gof.decimal = decimal.places)
  
}


# Use this function for each model


b_mod <- tex_reg_converter(b_mod)

ef_mod <- tex_reg_converter(ef_mod)

ed_mod <- tex_reg_converter(ed_mod)

```

Here is the output, with the standard errors in parentheses:

```{r, include = FALSE}
# Put tables all together

htmlreg(list(b_mod, ef_mod, ed_mod), stars = c(), caption = "Cox Model of Cabinet Durations", caption.above = TRUE, custom.model.names = c("Breslow", "Efron",  "Exact"), center = FALSE, single.row = TRUE)
```

<!DOCTYPE HTML PUBLIC "-//W3C//DTD HTML 4.01 Transitional//EN" "http://www.w3.org/TR/html4/loose.dtd">
<table cellspacing="0" style="border: none;">
<caption align="top" style="margin-bottom:0.3em;">Cox Model of Cabinet Durations</caption>
<tr>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b></b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Breslow</b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Efron</b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Exact</b></th>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Investiture</td>
<td style="padding-right: 12px; border: none;">0.38 (0.14)</td>
<td style="padding-right: 12px; border: none;">0.39 (0.14)</td>
<td style="padding-right: 12px; border: none;">0.41 (0.14)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Polarization</td>
<td style="padding-right: 12px; border: none;">0.02 (0.01)</td>
<td style="padding-right: 12px; border: none;">0.02 (0.01)</td>
<td style="padding-right: 12px; border: none;">0.02 (0.01)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Majority</td>
<td style="padding-right: 12px; border: none;">-0.57 (0.13)</td>
<td style="padding-right: 12px; border: none;">-0.58 (0.13)</td>
<td style="padding-right: 12px; border: none;">-0.62 (0.14)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Formation</td>
<td style="padding-right: 12px; border: none;">0.13 (0.04)</td>
<td style="padding-right: 12px; border: none;">0.13 (0.04)</td>
<td style="padding-right: 12px; border: none;">0.13 (0.05)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Post-Election</td>
<td style="padding-right: 12px; border: none;">-0.83 (0.14)</td>
<td style="padding-right: 12px; border: none;">-0.86 (0.14)</td>
<td style="padding-right: 12px; border: none;">-0.88 (0.15)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Caretaker</td>
<td style="padding-right: 12px; border: none;">1.54 (0.28)</td>
<td style="padding-right: 12px; border: none;">1.71 (0.28)</td>
<td style="padding-right: 12px; border: none;">1.86 (0.33)</td>
</tr>
<tr>
<td style="border-top: 1px solid black;">Log Likelihood</td>
<td style="border-top: 1px solid black;">-1299.89</td>
<td style="border-top: 1px solid black;">-1287.74</td>
<td style="border-top: 1px solid black;">-918.29</td>
</tr>
<tr>
<td style="border-bottom: 2px solid black;">N</td>
<td style="border-bottom: 2px solid black;">314</td>
<td style="border-bottom: 2px solid black;">314</td>
<td style="border-bottom: 2px solid black;">314</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;" colspan="5"><span style="font-size:0.8em"></span></td>
</tr>
</table>

### Table 4.5 

Let's compare the Cox Efron approximation with the Weibull proportional hazards. 

To convert from the A.F.T. to Prop. Hazards parameterization, we will use the ConvertWeibull function from Chap. 3. We will prepare the data the same way we did in Chap. 3.


```{r}

intercept <- rep(1, 314)

cabinet$intercept <- intercept

weib_mod1 <- survreg(dv ~ 0 + intercept + invest + polar + numst+ format + postelec
                     + caretakr, data = cabinet)

weib_mod2 <- survreg(dv ~ 0  + invest + intercept + polar + numst+ format + postelec
                     + caretakr, data = cabinet)

weib_mod1_ph <- ConvertWeibull(weib_mod1)

weib_mod2_ph <- ConvertWeibull(weib_mod2)

weib_ph <- rbind(weib_mod1_ph$vars, weib_mod2_ph$vars)


# Delete rows that are redundant/unnecessary 
weib_ph <- weib_ph[-c(1,2,9,12,13,14,15,16),]

weib_ph <- weib_ph[c("intercept", "invest", "polar", "numst", "format", "postelec",
                     "caretakr", "gamma"),]

weib_ph
```

Let's format this into a presentable table and compare it with the Cox Efron approximation. 

```{r, include = FALSE}
# Create texreg object for Weibull Prop. Hazards model 

coefficient.names <- c("Constant","Investiture", "Polarization", "Majority", "Formation", "Post-Election",
                       "Caretaker")
coefficients <- c(-3.86, .38, .02, -.60, .13, -.88, 1.73)
se <- c(.26, .14, .01, .13, .04, .14, .28)
shape <- 1.29
n <- 314
lik <- logLik(weib_mod1)
gof <- c(shape, lik, n)
gof.names <- c("Shape Parameter", "Log Likelihood", "N" )
decimal.places <- c(TRUE, TRUE, FALSE)

weib_mod_ph <- createTexreg(
  coef.names = coefficient.names, coef = coefficients, se = se,
  gof.names = gof.names, gof = gof, gof.decimal = decimal.places)

# Put Cox and Weibull tables together

htmlreg(list(ef_mod, weib_mod_ph), stars = c(), caption = "Cox and Weibull Estimates of 
        Cabinet Duration", caption.above = TRUE, custom.model.names = c("Cox", "Weibull"), center = FALSE, single.row = TRUE)
```



<!DOCTYPE HTML PUBLIC "-//W3C//DTD HTML 4.01 Transitional//EN" "http://www.w3.org/TR/html4/loose.dtd">
<table cellspacing="0" style="border: none;">
<caption align="top" style="margin-bottom:0.3em;">Cox and Weibull Estimates of 
        Cabinet Duration</caption>
<tr>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b></b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Cox</b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Weibull</b></th>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Investiture</td>
<td style="padding-right: 12px; border: none;">0.39 (0.14)</td>
<td style="padding-right: 12px; border: none;">0.38 (0.14)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Polarization</td>
<td style="padding-right: 12px; border: none;">0.02 (0.01)</td>
<td style="padding-right: 12px; border: none;">0.02 (0.01)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Majority</td>
<td style="padding-right: 12px; border: none;">-0.58 (0.13)</td>
<td style="padding-right: 12px; border: none;">-0.60 (0.13)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Formation</td>
<td style="padding-right: 12px; border: none;">0.13 (0.04)</td>
<td style="padding-right: 12px; border: none;">0.13 (0.04)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Post-Election</td>
<td style="padding-right: 12px; border: none;">-0.86 (0.14)</td>
<td style="padding-right: 12px; border: none;">-0.88 (0.14)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Caretaker</td>
<td style="padding-right: 12px; border: none;">1.71 (0.28)</td>
<td style="padding-right: 12px; border: none;">1.73 (0.28)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Constant</td>
<td style="padding-right: 12px; border: none;"></td>
<td style="padding-right: 12px; border: none;">-3.86 (0.26)</td>
</tr>
<tr>
<td style="border-top: 1px solid black;">Log Likelihood</td>
<td style="border-top: 1px solid black;">-1287.74</td>
<td style="border-top: 1px solid black;">-1014.62</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">N</td>
<td style="padding-right: 12px; border: none;">314</td>
<td style="padding-right: 12px; border: none;">314</td>
</tr>
<tr>
<td style="border-bottom: 2px solid black;">Shape Parameter</td>
<td style="border-bottom: 2px solid black;"></td>
<td style="border-bottom: 2px solid black;">1.29</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;" colspan="4"><span style="font-size:0.8em"></span></td>
</tr>
</table>
### Figure 4.1

In preparation for the plots, we mean center the polarization and
formation attempts covariates.

```{r, message = FALSE, warning = FALSE}

cabinet$polarmean <- cabinet$polar - mean(cabinet$polar)
cabinet$formmean <- cabinet$format - mean(cabinet$format)
```



We run Cox and Weibull models with these mean centered variables. We will use these models for out plots.  

```{r, results = 'hide'}

cox_mod_plot <- coxph(dv ~ invest + polarmean + numst + formmean + postelec + caretakr,
                 data = cabinet)

weib_mod_plot <- survreg(dv ~invest + polarmean + numst + formmean + postelec
                    + caretakr, data = cabinet)

```

We now calculate the baseline integrated hazard function, baseline survivor function, and baseline hazard function from the Cox model. 

```{r}

# Calculate baseline integrated hazard function H(t) 
haz_rte <- basehaz(cox_mod_plot, centered = FALSE)

# Convert H(t) to the baseline hazard, h(t). h(t) = H(t) - H(t-1) 

haz_cox <- data.frame(diff(haz_rte$hazard))

# Take out H(t) at t = 1 and merge with previous calculations

row <- data.frame(0.03594616)
colnames(row) <- "diff.haz_rte.hazard."
haz_cox <- rbind(row, haz_cox)
colnames(haz_cox) <- "baseline_hazard"

# Merge baseline hazards into master dataframe with integrated hazards
haz_rte$haz_cox <- haz_cox

# Calculate baseline survivor function
surv_basecox <- exp(-haz_rte$hazard)

# Merge baseline survivor values into master dataframe with integrated hazards
haz_rte$surv_basecox <- surv_basecox

```
```{r, include = FALSE}
haz_rte <- haz_rte[,c(2,1,3,4)]
```

```{r}
# A glimpse of the values for all three functions 
head(haz_rte)

```

We do the same for the Weibull model.  

```{r}


# Plot baseline survivor function for Weibull

# Let's create lambda from Weibull model

lambda_base <- unname(exp(-(weib_mod_plot$coef[1])))

# Because S(t) = exp(-(lambda*t))^p, we can generate the survivor function for the
# baseline case. 

p <- 1/weib_mod_plot$scale

t <- cabinet$'_t'

surv_baseweib <- exp(-(lambda_base * t)^p)

weib <- data.frame(cbind(t, surv_baseweib))

# We can also generate the baseline hazard function, knowing that 
# h(t) = lambda * p * (lambda * t)^(p-1)

haz_baseweib <- lambda_base * p * (lambda_base * t)^(p-1)

weib$haz_baseweib <- haz_baseweib

# The baseline integrated hazard is thus H(t) = -log(S(t))

inthaz_baseweib <- -log(surv_baseweib)

weib$inthaz_baseweib <- inthaz_baseweib

# A glimpse of the values for all three functions 

head(weib)

```

Using the values from the haz_rte and weib dataframes, we can plot the values for the baseline survivor, integrated hazard, and baseline hazards for both models. Let's start with the baseline survivor function. 

```{r}
base_surv <- ggplot(data = haz_rte, aes(x = time, y = surv_basecox, color = "black")) + geom_step() + geom_line(data = weib, aes(x = t, y = surv_baseweib, color = "red")) + 
  theme_bw() +
  ggtitle("Baseline Survivor Function") +
  xlab("Cabinet Duration") +
  ylab("") +
  labs(colour = "Model") +
  scale_color_manual(labels = c("Cox", "Weibull"), values = c("red", "black"))
```

Here is the integrated hazard function. 

```{r}

int_haz <- ggplot(data = haz_rte, aes(x = time, y = hazard, color = "black")) + geom_step() + geom_line(data = weib, aes(x = t, y = inthaz_baseweib, color = "red")) + 
  theme_bw() +
  ggtitle("Baseline Integrated Hazard Function") +
  xlab("Cabinet Duration") +
  ylab("") +
  labs(colour = "Model") +
  scale_color_manual(labels = c("Cox", "Weibull"), values = c("red", "black"))

```

Lastly, this is the baseline hazard. 

```{r}

#Drop last seven rows for graphical purposes

haz_rte <- haz_rte[-c(48:54),]

#Plot

base_haz <- ggplot(data = haz_rte, aes(x = time, y = haz_cox, color = "black")) + geom_step() + geom_line(data = weib, aes(x = t, y = haz_baseweib, color = "red")) + 
  theme_bw() +
  ggtitle("Baseline Hazard Function") +
  xlab("Cabinet Duration") +
  ylab("") +
  labs(colour = "Model") +
  scale_color_manual(labels = c("Cox", "Weibull"), values = c("red", "black"))

```

We can arrange all the plots together. 
```{r, message = FALSE}

grid.arrange(base_surv, int_haz, base_haz, ncol = 2)
```
