---
title: 'Chapter 6: Restrictive Abortion Legislation Data in R'
output: html_document
---

```{r, include = FALSE}
rm(list = ls())
options(stringsAsFactors = FALSE)
```

```{r, include = FALSE}

#---- Packages 
library(foreign)
library(survival)
library(survminer)
library(flexsurv)
library(texreg)
library(ggplot2)
library(SurvRegCensCov)

```

Let's load the dataset.

```{r}

#-------Dataset

adopt <- read.dta("~/Dropbox/github/liwu-gan.github.io/dta/adopt_singleevent.dta")

#-------Data prepation

# Create survival object for dv 

dv <- Surv(adopt$'_t', adopt$'_d')

```


### Table 6.1
First, we run each of the models. 

```{r}
# The conditional logit model is the same as the exact discrete method we used earlier

ed_mod <- coxph(dv ~ mooneymean, data = adopt, ties = "exact")

### Can't run Royston-Parmar model 


# Weibull P/H/
weib_mod <- survreg(dv ~ mooneymean, data = adopt, dist = "weibull")
```

Again, we have to convert the Weibull A.F.T. to a P.H. parameterization.
```{r}
# Conversion from Weibull A.F.T.  to P.H. 

intercept <- rep(1, 50)

adopt$intercept <- intercept

weib_mod1 <- survreg(dv ~ 0 + mooneymean + intercept, data = adopt)

weib_mod2 <- survreg(dv ~ 0 + intercept + mooneymean, data = adopt)

weib_mod1_ph <- ConvertWeibull(weib_mod1)

weib_mod2_ph <- ConvertWeibull(weib_mod2)

weib_ph <- rbind(weib_mod1_ph$vars, weib_mod2_ph$vars)

# Delete rows that are redundant/unnecessary 
weib_ph <- weib_ph[-c(1,2,4),]


weib_ph <- weib_ph[c("mooneymean", "gamma", "intercept"),]

weib_ph


```


Let's format these models into a presentable table.

```{r, include = FALSE}
# Create texreg object for Conditional Logit 

tex_reg_converter <- function(original_model){
  
  
  coefficient.names <- c("Pre-Roe")
  coefficients <- original_model$coef 
  se <- sqrt(diag(vcov(original_model)))
  n <- original_model$n
  lik <- logLik(original_model)
  gof <- c(lik, n)
  gof.names <- c("Log Likelihood", "N" )
  decimal.places <- c(TRUE, FALSE)
  
  createTexreg(
    coef.names = coefficient.names, coef = coefficients, se = se,
    gof.names = gof.names, gof = gof, gof.decimal = decimal.places)
  
}

ed_mod_final <- tex_reg_converter(ed_mod)
```
```{r, include = FALSE}
# Create texreg object for Weibull Prop. Hazards model 

coefficient.names <- c("Constant","Pre-Roe")
coefficients <- c(-2.10, -.22)
se <- c(.32, .08)
shape <- .98
n <- 50
lik <- logLik(weib_mod)
gof <- c(shape, lik, n)
gof.names <- c("Shape Parameter", "Log Likelihood", "N" )
decimal.places <- c(TRUE, TRUE, FALSE)

weib_mod_ph <- createTexreg(
  coef.names = coefficient.names, coef = coefficients, se = se,
  gof.names = gof.names, gof = gof, gof.decimal = decimal.places)

# Put Cox and Weibull tables together

htmlreg(list(ed_mod_final, weib_mod_ph), stars = c(), caption = "Models of Adoption of Restrictive Abortion Legislation", caption.above = TRUE, custom.model.names = c("Cox Model", "Weibull Model"), center = FALSE, single.row = TRUE)
```
<!DOCTYPE HTML PUBLIC "-//W3C//DTD HTML 4.01 Transitional//EN" "http://www.w3.org/TR/html4/loose.dtd">
<table cellspacing="0" style="border: none;">
<caption align="top" style="margin-bottom:0.3em;">Models of Adoption of Restrictive Abortion Legislation</caption>
<tr>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b></b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Cox Model</b></th>
<th style="text-align: left; border-top: 2px solid black; border-bottom: 1px solid black; padding-right: 12px;"><b>Weibull Model</b></th>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Pre-Roe</td>
<td style="padding-right: 12px; border: none;">-0.22 (0.09)</td>
<td style="padding-right: 12px; border: none;">-0.22 (0.08)</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">Constant</td>
<td style="padding-right: 12px; border: none;"></td>
<td style="padding-right: 12px; border: none;">-2.10 (0.32)</td>
</tr>
<tr>
<td style="border-top: 1px solid black;">Log Likelihood</td>
<td style="border-top: 1px solid black;">-96.60</td>
<td style="border-top: 1px solid black;">-133.07</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;">N</td>
<td style="padding-right: 12px; border: none;">50</td>
<td style="padding-right: 12px; border: none;">50</td>
</tr>
<tr>
<td style="border-bottom: 2px solid black;">Shape Parameter</td>
<td style="border-bottom: 2px solid black;"></td>
<td style="border-bottom: 2px solid black;">0.98</td>
</tr>
<tr>
<td style="padding-right: 12px; border: none;" colspan="4"><span style="font-size:0.8em"></span></td>
</tr>
</table>

### Figure 6.1 

We first calculate the baseline hazard for the Weibull. 
```{r}
# Let's create lambda from the Weibull model we ran earlier
  
lambda_base <- unname(exp(-(weib_mod$coef[1])))

p <- 1/weib_mod$scale

t <- adopt$'_t'

# We cangenerate the baseline hazard function, knowing that 
# h(t) = lambda * p * (lambda * t)^(p-1)

haz_baseweib <- lambda_base * p * (lambda_base * t)^(p-1)

weib <- data.frame(cbind(t, haz_baseweib))

```

We do the same for the Cox model we already ran earlier. 
```{r}
# Calculates integrated baseline hazard, H(t)

haz_rte <- basehaz(ed_mod, centered = FALSE)

# To get the baseline hazard, we calculate H(t) - H(t-1), which gives us the corresponding # value for all obs. except for the first. 

haz_cox <- data.frame(diff(haz_rte$hazard))

# Take out H(t) at t = 1 and merge with previous calculations

row <- data.frame(0.2208064)
colnames(row) <- "diff.haz_rte.hazard."
haz_cox <- rbind(row, haz_cox)
colnames(haz_cox) <- "baseline_hazard"

# Merge baseline hazards into master dataframe with integrated hazards

haz_rte$haz_cox <- haz_cox

#Drop last row for graphical purposes

haz_rte <- haz_rte[-c(16), ]

### Calculate baseline hazard rate for Royston-Parmar model

```

We are ready to plot now. 

```{r, message = FALSE}

ggplot(data = haz_rte, aes(x = time, y = haz_cox, color = "black")) + geom_step() +
  geom_line(data = weib, aes(x = t, y = haz_baseweib, color = "red")) + 
  theme_bw() +
  ggtitle("Hazard Functions") +
  xlab("Years Since Roe vs. Wade") +
  ylab("") +
  labs(colour = "Model") +
  scale_color_manual(labels = c("Cox", "Weibull"), values = c("red", "black"))

```


